Using WordNet and Short-Term Memory for Contextual Disambiguation

### 2016-11-18 Draft_1.tex
Continued additions to NLP section

\subsubsection{Text Preprocessing}
\label{sec:TextPreprocessing}
Before any analysis can take place, the inputted raw text must be converted into a usable format. This, once again, can be broken down into multiple steps\cite{NLPHandbook}:
\begin{itemize}
	\item Document Triage

@@

	\item Text Segmentation

@@

@@

\subsubsection{Lexical Analysis}
\label{sec:LexicalAnalysis}

\subsubsection{Syntactic Parsing}
\label{sec:SyntacticParsing}

\subsubsection{Semantic Analysis}
\label{sec:SemanticAnalysis}

\bibliography{references}
\bibliographystyle{IEEEtran}

>>>>

\subsubsection{Text Preprocessing}
\label{sec:TextPreprocessing}
Before any analysis can take place, the inputted raw text must be converted into a usable format. This, once again, can be broken down into multiple steps\cite{NLPHandbook}:
\begin{itemize}
	\item \textbf{Document Triage}

@@

	\item \textbf{Text Segmentation}

@@

\end{itemize} 
% ########################
% #  UNFINISHED SECTION  #
% ########################

\subsubsection{Lexical Analysis}
\label{sec:LexicalAnalysis}
One word can have multiple forms, for example "judge" (the lemma) has the forms \{"judge", "judges", "judging", "judged"\} (morphological variants).  The job of Lexical Analysis is to replace all morphological variants of a word, with their corresponding lemma, a process known as stemming \cite{NLPHandbook}.

% In terms of ease of token identification, it can be seen conceptually how this process is beneficial. With that said, when we consider the amount of information in a word, it can similarly be realised that we lose information about the form of a word, for example plural/singular and tense.
\subsubsection{Syntactic Parsing}
\label{sec:SyntacticParsing}
Whwn derviving meaning from sentances, the grammatical structure can provide important insight. The Syntactic parsing technique extracts this infomation using two processes \cite{NLPAlmostFromScratch}: 
\begin{itemize}
	\item \textbf{Part-of-speech Tagging}

	\begin{itemize}
		\item Each word is given tags denoting their syntactic role (e.g. noun/adjective/verb).
	\end{itemize}

	\item \textbf{Chunking}

	\begin{itemize}
		\item Noun phrases and verb phrases are detected and tagged using "begin chunk" and "inside chunk" labels
	\end{itemize}

@@

\subsubsection{Semantic Analysis}
\label{sec:SemanticAnalysis}
Semantics .

\newpage
\bibliography{references}
\bibliographystyle{IEEEtran}
